Learning to Synthesize Rules for Network Intrusion Detectors

### 2020-01-11 paper/paper.tex
pass on 4.3.3

\Mar{--------------------------- estou aqui}

Componente 3: Raridade dos contents \Fix{adicionar histograma}

Contents mais comuns recebem maior pontuação.
Nesse componente, para cada content da regra nós verificamos quão comum ele é. A pontuação é dada por:

\[\frac{\sum_{i=1}^{N}\frac{content\_frequency[content_i]}{max(content\_frequency)}}{N}\]

Onde 'N' é a quantidade de contents na regra.

Componente 4: Frequencia dos modificadores de content

>>>>

\subsubsection{Content rarity.} This heuristic weighs higher rules
that use popular strings in content options. More precisely, for a
given rule \tname{} takes the arithmetic mean of the popularity scores
of each content in that rule. More precisely, we calculate the
contribution of content rarity with the following formula:

\[\frac{\sum_{i=1}^{N}\frac{\mathit{content\_frequency[content_i]}}{\mathit{max(content\_frequency)}}}{N}\]

\noindent
, where $N$ is the number of content options in a given rule. Figure~\Fix{...elaborate...}

\Mar{----------------------------- parei aqui}

\subsubsection{Frequency of content modifiers.}
